Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 introduction.tex

Historically, the computing systems used by LHC experiments consisted of the
federation of a hundreds to thousands of distributed resources, %\textemdash{}
ranging in scale from small to mid-size resource~\cite{foster2003grid}. Although
the workloads to be executed are comprised of tasks that are independent of each
other, the management of the distribution of workloads across many heterogeneous
resources to ensure the effective utilization of resources and efficient
execution of workloads presents non-trivial challenges.

>>>>

Historically, the computing systems used by LHC experiments consisted of the
federation of hundreds to thousands of distributed resources, %\textemdash{}
ranging in scale from small to mid-size resource~\cite{foster2003grid}. Although
the workloads to be executed are comprised of tasks that are independent of each
other, the management of the distribution of workloads across many heterogeneous
resources to ensure the effective utilization of resources and efficient
execution of workloads presents non-trivial challenges.
